\section*{Experience}

\textbf{Lead Engineer} - Indonusa \\
\textit{Jan 2025 - Present}
\begin{highlights}
    \item Led a team in developing agriculture backoffice app
\end{highlights}

\textbf{Software Engineer} - DOT Indonesia \\
\textit{Aug 2022 - Present}
\begin{highlights}
    \item Built and maintained scalable web components using ReactJS and TailwindCSS.
    \item Successfully implemented design patterns to ensure code reusability and readblelity.
    \item Collaborated with designers and backend developers to deliver seamless, user-friendly experiences.
\end{highlights}

\textbf{Lead Engineer} - M-Knows Consulting \\
\textit{Feb 2023 - Jun 2023}
\begin{highlights}
    \item Led a team in developing modular and reusable components for a financial dashboard, enhancing project efficiency.
    \item Integrated APIs, ensuring seamless data flow and reducing system errors.
\end{highlights}

\textbf{Software Engineer} - Perjalanan Menembus Galaksi \\
\textit{May 2021 - Aug 2022}
\begin{highlights}
    \item Translated UI/UX designs into functional, responsive interfaces using Vue.js and TailwindCSS.
    \item Optimized website load time by implementing best practices in web performance.
\end{highlights}

\textbf{Software Engineer} - PT Telematric Integra \\
\textit{May 2019 - May 2021}
\begin{highlights}
    \item Developed and maintained web applications using jQuery, Laravel, CodeIgniter 3, and Bootstrap.
    \item Built responsive UI components and enhanced legacy systems to improve user experience and maintainability.
\end{highlights}
